Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-28 awipev-CO2.Rmd

seafet_depth_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_ctd,pHint_tot_sf)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
  dySeries("pHint_tot_sf", axis="y2", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

>>>>

seafet_depth_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_ctd,pHint_tot_sf)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
  dySeries("pH_s_seafet_temp_ctd", axis="y2", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
  dySeries("pHint_tot_sf", axis="y2", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
